### 2025-09-23 multiple-regression.qmd
20250911 - prevent R chunks in notes from running
20250923 - update

When the [outcome variable](#sec-correlationalStudy) is continuous, [linear regression](#sec-multipleRegressionLinear) is common.
However, there are other types of regression depending on type and distribution of the [outcome variable](#sec-correlationalStudy).
For instance, if the [outcome variable](#sec-correlationalStudy) is binary, [logistic regression](#sec-multipleRegressionLogistic) would be used.
If the [outcome variable](#sec-correlationalStudy) is an ordered categorical variable, [ordinal regression](#sec-multipleRegressionOrdinal) would be used.
If the [outcome variable](#sec-correlationalStudy) is a count, [Poisson](#sec-multipleRegressionPoisson) or [negative binomial](#sec-multipleRegressionNegativeBinomial) regression would be preferable.
If the [outcome variable](#sec-correlationalStudy) is a proportion, [beta regression](#sec-multipleRegressionBeta) would be used.

@@

```{r}
load(url("https://osf.io/download/fe37j/"))
```
:::

>>>>

When the [outcome variable](#sec-correlationalStudy) is continuous or semicontinuous, [linear regression](#sec-multipleRegressionLinear) is common.
However, there are other types of regression depending on type and distribution of the [outcome variable](#sec-correlationalStudy).
For instance, if the [outcome variable](#sec-correlationalStudy) is binary, [logistic regression](#sec-multipleRegressionLogistic) would be used.
If the [outcome variable](#sec-correlationalStudy) is an ordered categorical variable, [ordinal regression](#sec-multipleRegressionOrdinal) would be used.
If the [outcome variable](#sec-correlationalStudy) is a count, [Poisson](#sec-multipleRegressionPoisson) or [negative binomial](#sec-multipleRegressionNegativeBinomial) regression would be preferable.
If the [outcome variable](#sec-correlationalStudy) is a proportion, [beta regression](#sec-multipleRegressionBeta) would be used.

@@

load(url("https://osf.io/download/fe37j/"))
```
:::
